---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "vignettes/README-",
  fig.width = 10,
  fig.height = 4
)
```

# sohungry

[![Travis-CI Build Status](https://travis-ci.org/SCAR/sohungry.svg?branch=master)](https://travis-ci.org/SCAR/sohungry)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/SCAR/sohungry?branch=master&svg=true)](https://ci.appveyor.com/project/SCAR/sohungry)

## Overview

This R package provides access to the SCAR Southern Ocean Diet and Energetics Database, and some tools for working with these data. For more information about the database see http://data.aad.gov.au/trophic/.


### Installing

```{r eval=FALSE}
install.packages("devtools")
library(devtools)
install_github("SCAR/sohungry")
```

## Usage

Basic usage: load the desired dataset using `so_isotopes()`, `so_energetics()`, `so_lipids()`, `so_dna_diet()`, or `so_diet()`.

## Examples

```{r message=FALSE, warning=FALSE}
library(sohungry)
library(dplyr)
library(tidyr)
library(ggplot2)
```

### Isotopes

Load the stable isotope data:
```{r message=FALSE}
xi <- so_isotopes(format="mv")
```

Filter to taxon of interest, selecting d13C and d15N records:
```{r message=FALSE, warning=FALSE}
xi %>% dplyr::filter(taxon_name=="Electrona carlsbergi" & measurement_name %in% c("delta_13C", "delta_15N"))
```

### Diet

Load the diet data (stomach content analyses and similar):
```{r message=FALSE}
x <- so_diet()
```

A summary of what *Electrona carlsbergi* eats:
```{r message=FALSE}
x %>% filter_by_predator_name("Electrona carlsbergi") %>% diet_summary(summary_type="prey")
```

And what eats *Electrona carlsbergi*:
```{r message=FALSE}
x %>% filter_by_prey_name("Electrona carlsbergi") %>% diet_summary(summary_type="predators")
```

### Energetics

```{r message=FALSE}
xe <- so_energetics()
```

Select all single-individual records of *Electrona antarctica*:

```{r message=FALSE}
edx <- xe %>% filter(taxon_sample_count==1 & taxon_name=="Electrona antarctica")

## discard the dry-weight energy density values
edx <- edx %>% filter(measurement_units!="kJ/gDW")

## some data manipulation
edx <- edx %>%
  ## remove the spaces from the measurement names, for convenience
  mutate(measurement_name=gsub("[[:space:]]+", "_", measurement_name)) %>%
  ## convert to wide format
  dplyr::select(source_id, taxon_sample_id, measurement_name, measurement_mean_value) %>%
  tidyr::spread(measurement_name, measurement_mean_value)

## what does this look like?
edx
```

Plot the wet weight against wet-weight energy density:

```{r ea_plot1, message=FALSE}
p <- ggplot(edx, aes(wet_weight, energy_content))+geom_point()+theme_bw()+
  labs(x="Wet weight (g)", y="Energy density (kJ/g wet weight)")
plot(p)
```

Fit an allometric equation:

```{r ea_plot2, message=FALSE}
fit <- lm(log(energy_content)~log(wet_weight), data=edx)
px <- tibble(wet_weight=seq(from=min(edx$wet_weight), to=max(edx$wet_weight), length.out=51))
px$energy_content <- exp(predict(fit, newdata=px))
p+geom_path(data=px, colour="dodgerblue")
```


### Lipids and fatty acids

```{r message=FALSE}
xl <- so_lipids()
```

Select lipid-class data from Connan et al. (2007), and plot similar to Figure 2 from that paper:

```{r lip_plot1, message=FALSE}
xl <- xl %>% dplyr::filter(source_id==126 & measurement_class=="lipid class") %>%
  mutate(measurement_name=sub(" content", "", measurement_name)) ## tidy the names a little

ggplot(xl,
  aes(measurement_name, measurement_mean_value, fill=taxon_life_stage, group=taxon_life_stage))+
  geom_col(position="dodge")+theme_bw()+
  labs(x="Lipid class", y="Percentage of lipids")
```
